---
title: "Getting Started with BioAnchor"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with BioAnchor}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## Overview

`bioanchor` lets you permanently archive MCMC analysis metadata on the 
[Arweave](https://arweave.org) permaweb. It extracts convergence diagnostics,
posterior summaries, and model specifications from fitted model objects, then
uploads them as structured JSON.

## Basic Workflow

```{r example}
library(bioanchor)
library(posterior)

# Use the built-in eight schools example
draws <- example_draws("eight_schools")

# Extract metadata
meta <- extract_metadata(draws, model_name = "eight_schools_demo")
print(meta)
```

## Archiving with Mock Uploader

For testing (no Arweave wallet required):

```{r mock}
result <- archive_mcmc(draws, model_name = "eight_schools_demo")

# Inspect the result
result$upload$tx_id
result$upload$payload_size
```

## Adding Custom Metadata

```{r extra}
meta <- extract_metadata(draws,
  model_name = "eight_schools",
  extra = list(
    author = "Dohoon Kim",
    affiliation = "Promptgenix LLC",
    project = "Hierarchical model comparison",
    doi = "10.5281/zenodo.19709077"
  )
)
```

## Real Arweave Upload

When you have an Arweave JWK wallet:

```{r real-upload, eval = FALSE}
result <- archive_mcmc(draws,
  model_name = "eight_schools",
  jwk_path = "~/.arweave/wallet.json",
  extra = list(author = "Your Name")
)

# Access the permanent URL
browseURL(result$upload$url)
```
